Interpolate the weight at agecl output to annual age

### 2020-06-03 InterpolateWeightAtAge.Rmd
final dataset in atlantisom form

  # complex, but works for 2 ages/agecl, need to test, need to fix oldest
  wtage_out <- wtage_out %>%
    dplyr::select(species, time, trueage, agecl, avgage) %>%
    dplyr::left_join(wtagecl_inc) %>%
    dplyr::group_by(species, time) %>%
    dplyr::mutate(wtIntage = case_when(
      trueage==1 ~ trueage/avgage*increment,
      (trueage>1 & trueage<avgage) ~ 
        (1-(avgage-trueage)/avgageinc)*increment + lag(atoutput),
      (trueage>1 & trueage>avgage) ~ 
        ((trueage-avgage)/lead(avgageinc))*lead(increment) + atoutput
        ))

@@

>>>>

  # complex, but works for 2 ages/agecl, need to test more, need to fix oldest
  wtage_out <- wtage_out %>%
    dplyr::select(species, time, trueage, agecl, avgage) %>%
    dplyr::left_join(wtagecl_inc) %>%
    dplyr::group_by(species, time) %>%
    dplyr::mutate(wtIntage = case_when(
      trueage==1 ~ trueage/avgage*increment,
      (trueage>1 & trueage<avgage) ~ 
        (1-(avgage-trueage)/avgageinc)*increment + lag(atoutput),
      (trueage>1 & trueage>avgage) ~ 
        ((trueage-avgage)/lead(avgageinc))*lead(increment) + atoutput
        ))

@@

  # fix oldest age

  #clean up to have only standard columns
  finaldata <- data.frame("species" = wtage_out$species,
                          "agecl" = wtage_out$trueage, "polygon" = NA, "layer" = NA,
                          "time" = wtage_out$time, "atoutput" = wtage_out$wtIntage)
